### 2020-01-30 wuhan.tex
pullpush

Here, we show that a wide range of approaches to estimating \Ro\ present a simple framework for evaluating uncertainties 
associated with the estimates of $\mathcal R_0$
across a wide range of models using a generation-interval based approach and compare early estimates of $\mathcal R_0$ of the 2019-nCoV outbreak.
Our results indicate that most early estimates of $\mathcal R_0$ for the outbreak
are likely to have been overly confident.

>>>>

Here, we show that a wide range of approaches to estimating \Ro\ can be understood and compared in terms of estimates for three quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$. We argue that authors should make sure their assumptions about these three quantities are clear and reasonable, and that estimate uncertainty should propagate error from all three sources.

We evaluate six disparate models posted online in daterange that estimated \Ro\ for the 2019-nCoV outbreak. <C-F3>
Our results indicate that most early estimates of $\mathcal R_0$ for the outbreak
are likely to have been overly confident.
